\bf\mftitle

### 2011-01-26 doc/jInfer/base/base.tex
Some cite{} corrections to base

Description of \jmodule{Base} structure will partially mirror its JavaDoc documentation. For more detailed information, refer to it directly.\\

\jmodule{Base} contains logic for Log4j initialization in \code{Installer} class. Configuration of the overall logging granularity level (NetBeans options integration) is contained in \code{cz.cuni.mff.ksi.jinfer.base.options} package. Shared jInfer graphics is contained in the \code{cz.cuni.mff.ksi.jinfer.base.graphics} and \code{cz.cuni.mff.ksi.jinfer.base.graphics.icons} packages.

@@

Regular expression representation is contained in \code{cz.cuni.mff.ksi.jinfer.base.regexp} package. Most important class is of course \code{Regexp}, assisted by an enum of its type \code{RegexpType} and representation of its interval \code{RegexpInterval}.\\
XML node representation is described by interfaces in \code{cz.cuni.mff.ksi.jinfer.base.interfaces.nodes} package and more-less concrete implementations in \code{cz.cuni.mff.ksi.jinfer.base.objects.nodes} package.\\
Finite state automata representation is contained in the \cite{cz.cuni.mff.ksi.jinfer.base.automaton} package.\\
Refer to \ref{archdoc} to get an accurate description of all these representations.\\

@@

Apart from interfaces contained in already discussed \code{cz.cuni.mff.ksi.jinfer.base.interfaces.nodes} package, there is an important group of interfaces contained in \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference} package: the \emph{inference} interfaces. They come in two flavours: the actual inference interface, and its callback. For a comprehensive description of them and their interaction refer again to \ref{archdoc}.\\

@@

This is not an inference module and there is no real data flow in it. Refer to \ref{archdoc} to understand the inference process described by interfaces from \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference} package.

@@

%\nocite{*}
\newpage
\bibliographystyle{alpha}
\bibliography{literature}

>>>>

Description of \jmodule{Base} structure will partially mirror its JavaDoc documentation (\cite{javadoc}). For more detailed information, refer to it directly.\\

\jmodule{Base} contains logic for Log4j (\cite{log4j}) initialization in \code{Installer} class. Configuration of the overall logging granularity level (NetBeans options integration) is contained in \code{cz.cuni.mff.ksi.jinfer.base.options} package. Shared jInfer graphics is contained in the \code{cz.cuni.mff.ksi.jinfer.base.graphics} and \code{cz.cuni.mff.ksi.jinfer.base.graphics.icons} packages.

@@

Regular expression representation is contained in \code{cz.cuni.mff.ksi.jinfer.base.regexp} package. Most important class is of course \code{Regexp}, assisted by an enum of its type \code{RegexpType} and representation of its interval \code{RegexpInterval}.\\
XML node representation is described by interfaces in \code{cz.cuni.mff.ksi.jinfer.base.interfaces.nodes} package and more-less concrete implementations in \code{cz.cuni.mff.ksi.jinfer.base.objects.nodes} package.\\
Finite state automata representation is contained in the \code{cz.cuni.mff.ksi.jinfer.base.automaton} package.\\
Refer to \cite{archdoc} to get an accurate description of all these representations.\\

@@

Apart from interfaces contained in already discussed \code{cz.cuni.mff.ksi.jinfer.base.interfaces.nodes} package, there is an important group of interfaces contained in \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference} package: the \emph{inference} interfaces. They come in two flavours: the actual inference interface, and its callback. For a comprehensive description of them and their interaction refer again to \cite{archdoc}.\\

@@

This is not an inference module and there is no real data flow in it. Refer to \cite{archdoc} to understand the inference process described by interfaces from \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference} package.

@@

\nocite{*}
\newpage
\bibliographystyle{alpha}
\bibliography{literature}
